Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2019-02-07 ms5n17-tlp-mn-180216-001.tex
fixed figure caption

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png} 
\caption{Drawings of the detector assembly and the microfluidic device (1) in (A) front view and, (B) exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In (A), PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
\label{fig:rf-device-assembly}
\end{figure}

>>>>

In the remainder of this paper, we discuss the probe design in more detail,
and characterise its performance in terms of sensitivity and resolution.
We also demonstrate its application in microfluidic cell culture,
protein NMR spectroscopy, and micro-imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Probe Design}
\label{sec:probe-design}
%Figure showing modular probe concept; example of probe base with several inserts\newline
%\begin{itemize}
%	\item Philosophy: use cheap materials and prefab Al profiles wherever possible
%	\item Hold it together with a small number of precision-machined parts
%	\item Generic probe base design that can accommodate a variety of inserts
%	\item Insert: PCB that accommodates both tuning/matching circuitry for up to two channels and the transmission line probe itself
%	\item Tuning and matching capacitors for each channel are part of the probe base
%	\item Connection using standard coaxial RF connectors (SMP)
%	\item Microfluidic chip design; outline
%	\item Design/explosion drawings
%	\item Circuit design for double resonance
%	\item Transmission line connection between tuning/matching of 1H channel and resonator (Smith chart argument)
%	\item 38 mm bore (Bruker NB) and 45 mm bore (Varian/Agilent NB)
%\end{itemize}
\begin{figure}
\centering
\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-190205-rf-device-assembly.png}
\caption{Drawings of the detector assembly and the microfluidic device (1). A: front view; B: exploded view. Spacer (4) ensures the alignment of the sample chamber with the constrictions on the PCB planes. In A, PCB plane 5 is hidden to show the orientation of 1 with respect to PCB plane 3.}
\label{fig:rf-device-assembly}
\end{figure}
